Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy

### 2020-01-21 manuscript/supplement.Rmd
Change affiliation

---
title: "Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Supplement to Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Brigham Young University
  email: andrew_heiss@byu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

>>>>

---
title: "Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Supplement to Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---
